---
title: "Investigating COVID-19 Virus Trends"
author: "Joshua Goldberg"
date: "7/27/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readr)
library(tibble)
```

## Summary
During this project I analyzed COVID-19 data metrics collected between January and June, 2020 to understand positive test result rates over time.
Through this analysis, I discovered that the three countries with the greatest proportion of positive test results were the United Kingdom, United States of America and Turkey.

## Goal
The goal of this project is to identify which countries have had the greatest proportion of positive COVID-19 Test Results. In addition to the information from the Summary, I was able to analyze this information more to understand how COVID data results have changed over time.


```{r Analysis, echo = TRUE, include = TRUE}

#1/2 - Load in the Dataset
covid_df <- read_csv("C:/Users/Goldbej6/Desktop/Learning/R/covid19.csv")

#3 - Dimension of Dataframe
dim(covid_df)

#4 - Evaluating Column Names
vector_cols <- colnames(covid_df)
vector_cols
vector_cols_class <- class(vector_cols)

#5 - Viewing the data 
data_head <- head(covid_df)

#6 - Summary of dataset
glimpse(covid_df)

#7 - Filtering and Selecting Columns of Interest 
covid_df_all_states <- covid_df %>% 
  filter(Province_State == "All States") %>% 
  select(-Province_State)

#8 - Select specific columns
covid_df_all_states_daily <- covid_df_all_states %>% 
  select(Date, Country_Region, active, hospitalizedCurr, daily_tested, daily_positive)

#9 - Country Daily Totals
covid_df_all_states_daily_sum <- covid_df_all_states_daily %>% 
  group_by(Country_Region) %>% 
  summarize(tested = sum(daily_tested),
            positive = sum(daily_positive),
            active = sum(active),
            hospitalized = sum(hospitalizedCurr)
    ) %>% 
  arrange(-tested)

covid_df_all_states_daily_sum

#10 - Top rows
covid_top_10 <- covid_df_all_states_daily_sum %>% 
  head(10)


#11 - Create vectors
countries <- covid_top_10$Country_Region
tested_cases <- covid_top_10$tested
positive_cases <- covid_top_10$positive
active_cases <- covid_top_10$active
hospitalized_cases <- covid_top_10$hospitalized

#12 - renaming vectors
names(tested_cases) <- countries
names(positive_cases) <- countries
names(active_cases) <- countries
names(hospitalized_cases) <- countries

#13 - Top proportion results
posvstest <- positive_cases/tested_cases
positive_tested_top_3 <- sort(posvstest)
positive_tested_top_3 <- c("UK" = 0.113, "US" = 0.109, "Turkey" = 0.081)
positive_tested_top_3


#14 - Creating vectors
united_kingdom <- c(0.11, 1473672, 166909, 0, 0)
united_states <-  c(0.10, 17282363, 1877179, 0, 0)
turkey <-  c(0.08, 2031192, 163941, 2980960, 0)

covid_mat <- rbind(united_kingdom, united_states, turkey)
colnames(covid_mat) <- c("Ratio", "tested", "positive", "active", "hospitalized")
covid_mat

#15 - Question variable
question <- "Which countries have had the highest number of positive cases against the number of tests?"

#16 - Answer variable
answer <- c("Positive tested cases" = positive_tested_top_3)

#17 - Answer List
dataframe_list <-  list(covid_df, covid_df_all_states, covid_df_all_states_daily, covid_top_10)
matrices_list <- list(covid_mat)
vectors_list <- list(vector_cols, countries)
data_structure_list <- list("dataframe" = dataframe_list, "matrix" = matrices_list, "vectors" = vectors_list)
data_structure_list

#18 - Combined List
covid_analysis_list <- list(question, answer, data_structure_list)
covid_analysis_list[[2]]

```

